\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myAcontent}[0]{
The Penske-Wynn showroom is in Las Vegas in a famous hotel. The people who stay at the hotel want to win lots of money at Las Vegas and become rich. Now they are not rich. They cannot buy the cars in the showroom. But they want to look at them. The problem was that there were so many people just looking at the cars.
}

\newcommand{\myBcontent}[0]{
Penske-Wynn charged an entrance fee of 10 dollars (350 NT). It also started selling Ferrari products in a Ferrari Store. This was the first Ferrari Store in the US. A Ferrari T-shirt costs 50 dollars (1800 NT). A Ferrari skateboard costs 170 dollars (6000 NT)
}

\newcommand{\myCcontent}[0]{
The showroom is very, very popular. It makes almost 100,000 dollars a month. The Ferrari store is also successful. But it is less successful than the showroom. People think the prices are expensive. But many people still buy the products.
}

\newcommand{\myDcontent}[0]{
The experiment with the showroom and the Ferrari Store was successful. There are no other showrooms with an entrance fee. But there are now 3 or 4 more Ferrari Stores in other cities in America. They sell clothes, shoes, toys and car accessories.
}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{}{cars 2}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{}{cars 2}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{}{cars 2}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{}{cars 2}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{}{cars 2}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{}{cars 2}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{}{cars 2}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{}{cars 2}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


