\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
graham 4
}

\newcommand{\myAcontent}[0]{
It's important to have clear goals, running a business or writing software. It is very difficult to plan, because you can't see the future, but you need to be very clear about your goals. It is also very important to talk to the users, at the same time as you plan. You need to see what they think. Their feedback will help you plan.

}

\newcommand{\myBcontent}[0]{
Writing down business plans is hard work, but they should continually be kept up to date. The hard work writing down the business plan is a waste of time, if you don't keep them up to date. If you do keep them up to date, they can be shown to banks and investors. Keeping them up to date also helps you to decide on what the business's next moves are.

}

\newcommand{\myCcontent}[0]{
In the fastest-growing businesses, everyone feels the company's goals are their own goals. But you can't tell people what the plan is and expect them to get excited about it.  People will get excited about the boss's goals, and their own role in the plans, only when they feel they are involved in creating the plans and the plans have new goals for them.

}

\newcommand{\myDcontent}[0]{
William Kendall couldn't sell his previous company, because people thought they wouldn't run it as well as him. So, starting his next company, he immediately started thinking how to sell it. He went to a very big company, and asked them if they wanted to invest ten percent. They did. And now the big company has bought all of his company. That was his plan.

}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


