\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
stress
}

\newcommand{\myAcontent}[0]{
I think we should offer a free medical check-up every year, and bring in Alan Bradshaw, to help with the stress levels.

He could identify stress hotspots in the company and raise managers awareness of stress and train them in ways to reduce the stress they put on their staff. 

We have a company nurse, but she can't identify causes of stress.
}

\newcommand{\myBcontent}[0]{
We should improve the food in the company cafeteria. The food here isn't healthy.

And it is not good for people's stress levels, the way drinking coffee or coke can make you feel more tense and excited.

To reduce these levels, we need to have more natural foods, like fish, fruit and vegetables, in the cafeteria.
}

\newcommand{\myCcontent}[0]{
I think everyone should be involved in a lot of physical activity, like jogging, or swimming, or basketball.

It would be nice to have our own basketball court and swimming pool, but that would be very expensive.

Instead, I think we should arrange a group membership for everyone at the local sports center. The center is expensive, but good.

}

\newcommand{\myDcontent}[0]{
We should have company tours. Every month, we should all go to an amusement park, or climb a mountain.

Once or twice a year, we should travel overseas. I think it would be fun to go to Korea.

When people are having fun, they can forget about work, and they will come back with good feelings about the company.

}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{1}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{1}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{1}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{1}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{1}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{1}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{3}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{1}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


