\documentclass[b5paper]{article}
\usepackage{color}
\usepackage{multicol}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.30cm}{0.35cm} %HPDeskJet5160
\textblockorigin{0.00cm}{0.15cm} %HPDeskJet5160
\setlength{\unitlength}{1cm}
\usepackage{xeCJK}
\setCJKmainfont{WenQuanYi Zen Hei}
\pagestyle{empty}

\newcommand{\myIdentifier}[0]{
Festival survey
}

\newenvironment{enumerate*}%
{\begin{enumerate}%
 \setlength{\itemsep}{0pt}%
 \setlength{\parsep}{0pt}%
 \setlength{\parskip}{0pt}}%
{\end{enumerate}}

% \renewcommand{\labelitemi}{$\bullet$}

\newcommand{\myContent}[0]{

\setlength{\leftmargini}{+0.5cm}

\begin{multicols}{3}

\begin{enumerate*}
\item    When is the holiday celebrated?
\item    Is it celebrated as a family or a group?
\item    When does the celebration for this holiday generally start?
\item    Is it a religious holiday?
  \item  Are there special foods connected with the holiday?
  \item  Is gift giving a part of this holiday?
  \item  What is done to show that this holiday is being observed?
  \item  Is it strictly an American holiday?
  \item  What does the holiday stand for? Why is this holiday celebrated?
  \item  Are the banks, post offices or schools closed for this holiday?
  \item  Is there is a person or god connected with the holiday?
  \item Are there special songs associated with the holiday?
  \item Do schools, temples or churches have special programs for this holiday?
  \item Are there parties?
  \item Do you see your relatives during this holiday?
  \item How many different ethnic groups celebrate this holiday?
  \item What do you usually do for this holiday?
  \item Are cards sent or given for this holiday?
  \item What traditional colors are associated with this holiday?
  \item What holidays have disappeared in your country?
  \item What is your parent's favorite holiday?
  \item What new holiday are needed in your country?
  \item What holiday should be abolished?
  \item What are some of your fondest memories of Thanksgiving?
  \item What kind of traditional food do you eat for Thanksgiving?
  \item Where is the best place to be for the holidays?
  \item Do you think holidays are important? Why?
  \item What kinds of thing do you like to do on the holidays?
  \item How many holidays do you have in your country?
  \item What special foods are associated with your favorite holiday?
  \item What special clothing/customs are associated with your favorite holiday?
  \item What is your favorite holiday memory? Tell us about it.
  \item Who is your favorite holiday character (e.g. Santa Claus)? Why?
  \item What are three holidays that you like to spend with your family?
  \item What is your worst holiday memory? Tell us about it.
  \item Do you like to stay up late on holidays?
\end{enumerate*}

\end{multicols}
}

\newcommand{\mycard}[2]{%
	\vspace{0.1cm}
	\large #1
	\par
	\begin{minipage}[c][11.9cm][c]{16.1cm}%
	\normalsize #2
	\end{minipage}
}

\begin{document}

\begin{textblock}{16}(0,0)
\textblocklabel{picture1}
\mycard{\myIdentifier}{\myContent} 
\end{textblock}

\begin{textblock}{16}(0,8)
\textblocklabel{picture5}
\mycard{\myIdentifier}{\myContent}
\end{textblock}

\end{document}


