\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.10cm} % HPLaserJet2300
% \textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
oliver 2
}

\newcommand{\myAcontent}[0]{
Charles is the CEO of the camping equipment company. Todd, the marketing manager, and Oliver, a salesman. are fighting. Charles wants Todd and Oliver to stop fighting, but he doesn't know what to do. Todd is right, and Oliver is wrong, but he doesn't want to make Oliver unhappy. He doesn't want Oliver to leave the company, because he is a very good salesman.
}

\newcommand{\myBcontent}[0]{
Jack, the production manager doesn't like Oliver. Oliver just thinks about what he wants, rather than what is good for the company. He promises delivery dates to customers that are impossible. He expects Jack to produce the products in time. Jack cannot do this. Jack wants him to leave the company. Jack is unhappy that Charles and Todd don't fire Oliver.
}

\newcommand{\myCcontent}[0]{
Oliver is a super salesman. He loves selling to customers. He has decided to leave the company, because Jack and Todd do not respect his hard work. He can get orders, but the company cannot take the orders, because Jack does not try to increase production. Todd only tries to control him. Todd makes him write useless reports and telephone messages.
}

\newcommand{\myDcontent}[0]{
Todd is the manager of the sales team. He thinks Oliver may be hurting the company. He only thinks about his own job, not about what other people have to do. He doesn't help the other sales people by telling them about his customers. Todd thinks he may want to leave the company and set up his own company. Todd doesn't want him to leave the company.
}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


