\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
super salesman
}

\newcommand{\myAcontent}[0]{
You are Charles, the CEO of the camping equipment company. The company is very successful, because you have a good sales team. Todd is the marketing manager. Oliver is a super salesman. Todd and Oliver are fighting. Oliver won't cooperate with Todd. You want to help Todd and Oliver stop fighting. And you don't want Oliver to leave the company.
}

\newcommand{\myBcontent}[0]{
You are Jack, the production manager. You don't like Oliver. He promises delivery dates to customers that are impossible. He does not understand that the company cannot produce the products in time. He just thinks about what he wants, rather than what is good for the company. You want him to leave the company.
}

\newcommand{\myCcontent}[0]{
You are Oliver. You are a super salesman. It is very exciting. You love getting customers to buy your products. You have decided to leave the company, because you do not get any respect from Jack, Todd and the other people for your hard work. They don't try to help you be a better salesman. They just try to control what you are doing.
}

\newcommand{\myDcontent}[0]{
You are Todd. You are the manager of the sales team. Jack only thinks about his own job, not about what other people have to do. He doesn't help the other sales people and he doesn't want you to know about his customers. You don't want him to leave the company, but you think he may be hurting the company.
}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


