\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
candidate 2
}

\newcommand{\myAcontent}[0]{
These criteria will be used to choose the candidate: 1. a natural leader,2. most energetic, confident and outgoing, 3. best sales record, 4. best organizational skills, 5. best academic record, 6. most knowledge of languages,
}

\newcommand{\myBcontent}[0]{
Barbara has a UNIVERSITY DEGREE and has worked at Fast-Track for 12 years. She had the best sales record for the last 5 years. She knows Polish and Russian, but is not very fluent in English. She is energetic, confident. But sometimes is aggressive. She may not be a good leader.
}

\newcommand{\myCcontent}[0]{
Tadeusz ONLY FINISHED HIGH SCHOOL but has worked in many industries, although NONE OF THESE WAS IN SALES. He joined Fast-Track 5 years ago as sales manager for the south of Poland. He increased sales 12\% over the 5 years. He is a hard worker, but not outgoing. His team think he is a good leader.
}

\newcommand{\myDcontent}[0]{
Eva has a university degree in history, and worked for 15 years in sales. She has been with Fast-Track for 1 year. She had a good sales record before, but only a satisfactory one now. She speaks German, English, Polish. She is quiet. She might be a good leader, but might be too dependent.
}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


