\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
Nicholson's advice
}

\newcommand{\myAcontent}[0]{
Nicholson says the manager needs to help the two different teams find ways in which they agree, for example, about concern for family, the need for respect, the desire to do a good job. On the basis of this agreement they can start to agree about how to work together as one sales team, too. Important people to lead this process are people who disagree with their own team.
}

\newcommand{\myBcontent}[0]{
Nicholson advises managers who support one team rather than the other team to examine their own and the other people's motivation. Todd needs to understand why Oliver wants to be a super salesman. He also needs to understand the real reason he wants to control Oliver. The old Peterson sales manager needs to understand the real reason he (or she) supports the Peterson team.
}

\newcommand{\myCcontent}[0]{
Nicholson thinks Oliver and the Muller sales team aren't able to see the big picture. They are just thinking about selling the product and they don't think about production of the product. They probably don't realize that the company is a system, where everyone needs to cooperate and everyone needs to have all the information available, so that the system works well.
}

\newcommand{\myDcontent}[0]{
Nicholson thinks the Peterson sales team understands the big picture. It understands it is part of the company, which is a system. It also understands the company is part of a larger system with its customers. He thinks it may not realize it is the most important part of the company. Contact with larger systems through customers determines the success of the company.
}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


