\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
MPM 2
}

\newcommand{\myAcontent}[0]{
Before, you were the Muller Sales Manager. Now you are Sales Manager of the new MPM team. The two sales teams were very different. You will lead a meeting to help the 2 teams work together. Listen to the sales people's opinions and find a plan which will improve the atmosphere in the department and help staff be effective. You think the Muller sales reps are better sales people.

}

\newcommand{\myBcontent}[0]{
A year ago, you were the Peterson sales manager. Now you are the MPM Deputy Sales Manager.

The two sales teams are very different. A meeting is going to be held so two teams can work together effectively. A, as Sales Manager, will lead the meeting, and you, as Deputy Sales Manager, will help him/her.

You think the Peterson sales reps are better.

}

\newcommand{\myCcontent}[0]{
You are the old Muller sales team in the new company, MPM. 
You want to make as much money as possible. You promise early delivery dates, even if the company cannot meet the date, and customers complain.
Your sales reports are often late and incomplete.
You keep information to yourself, rather than share it with co-workers.
You aggressively put pressure on customers to buy, and give them expensive gifts.

}

\newcommand{\myDcontent}[0]{
You are the old Peterson sales team in the new company, MPM. 
You are interested in working as a team, not how much money you make.
You believe the company should always meet its delivery dates.
You want a higher basic salary and bonuses if you exceed the monthly target.
You share information about customers to maximize sales.
You do not put pressure on customers to buy, or give them expensive gifts.

}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


