\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{color}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
% \usepackage[absolute,showboxes]{textpos}
\usepackage[absolute]{textpos}
\TPMargin{0.2cm}
% \usepackage{CJK}
\usepackage{pifont}
\usepackage{amsfonts}
% \textblockorigin{0.30cm}{0.35cm} %HPDeskJet810C
% \textblockorigin{0.30cm}{3.35cm} % LaserJet
\textblockorigin{0.05cm}{0.05cm} % HPLaserJ5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}
\renewcommand{\baselinestretch}{0.5}

\begin{document}
% \begin{CJK}{UTF8}{song}

\TPshowboxestrue
\begin{textblock}{7.5}(8,3.2)
\large On the \textbf{seating chart}, write down for the group:
\begin{description}
\item [Number of group] For example, 1 for the first group, 2 for the next group.
\item [Exercise ID] The small letters at the top left hand side of the A,B,C,D cards. For example, Krystal 4.
\end{description}
\end{textblock}
\TPshowboxesfalse

\TPshowboxestrue
\begin{textblock}{7.5}(8,5.3)
\large After collecting \textbf{answer cards}:
\begin{description}
\item [Each set of 3 cards] Put \textbf{A}'s card 1st, \textbf{B}'s 2nd, \textbf{C}'s 3rd, And write the \textbf{group} name on the 1st card. Write the \textbf{Exercise ID} also, if it's not there.
\item [Cards with same Exercise ID] Put them \textbf{together} in alphabetical order according to \textbf{group}.
\item [All cards] Put them together in alphabetical order according to \textbf{Exercise ID.}
\end{description}
\end{textblock}
\TPshowboxesfalse

\begin{textblock}{14}(1,1)

\Huge == Stage 1: Reading\\

\large \mdseries
Group is directed to right seat, A, B, C, D and sits down.\\

\begin{description}

\item [Card handler] Distributes role cards according to the \textbf{seating chart}\\
\item [Announcer]
\Large \bfseries
	"XXX is A, YYY is B, ZZZ is C, WWWW is D."\\
	...\\
	"Go. You have one minute."\\
\large \mdseries
\item [Timer]	Starts stop watch.\\
	Stops watch after 1 minute.\\
	Tells Announcer.\\

\end{description}

\Huge == Stage 2: Speaking\\

\large \mdseries

\begin{description}

\item [Announcer]
\Large \bfseries
	"Stop.\\
	Put the cards down.\\
	Put the pens down.\\
	Stand up.\\
	--\\
	Go. You have 3 minutes."\\
	% Go. You have 1 minute."\\

\large \mdseries
\item [Card handler]
	Collects role cards.\\
	Listens for Chinese use.\\
	Takes pens from students.\\
	Gives out answer cards \textbf{after 1 minute.}\\
\item [Timer]
	Starts stop watch.\\
	Tells examiners when 1 minute (and 3 minutes) has passed.\\

%\huge == Stage 2 Part 2: After 1 minute
%(With question cards)\\
%
%\large \mdseries
%\item [Card handler]
%	Gives out question cards.\\
%\item [Timer]
%	Stops watch after another 2 minutes.\\

If someone uses Chinese, the card handler
talks with the Announcer, who says: "No Chinese!", and marks
the name of the Chinese user on the seating chart each time he/she uses Chinese.

I will grade you for your work as an examiners. If I see no record of Chinese use on the seating chart (or all zeros), I will think you didn't do a good job and I \textbf{won't} give you a grade of 5.

So listen to the conversation!! Are they using Chinese??

\end{description}

\Huge == Stage 3: Answering\\

\begin{description}

\large \mdseries
\item [Announcer]
\Large \bfseries
	"Stop.\\
	Sit down.\\
	--\\
	Names and IDs. Write your names and IDs at the top.\\
	--\\
	% Go. You have 10 seconds."\\
	Go. You have 1 minute."\\
	--\\
	Stop. Give me your cards."\\

\large \mdseries
The card handler puts the answer cards together with the role cards with a big paper clip. Then the paper handler prepares the cards for the next group.

\end{description}

\Huge == Notes\\

\large \mdseries
Any question you have or the students ask you and you're not too sure how to answer, please shout out:\\
\Huge \bfseries
	"Dr Bean/Greg! We have a question!"

\end{textblock}

% \end{CJK}
\end{document}
