\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
hotels 1
}

\newcommand{\myAcontent}[0]{
The Morocco hotel is a 5-star hotel near the beach. Inside the hotel, it is very nice with a large swimming pool and a nightclub. There are also gardens, shops and a sauna. The price of the hotel is 1,500 dollars. There are two large conference rooms, but no seminar rooms. Perhaps special interest groups could meet in the gardens. It is a long, one-hour drive to the airport and to the nearest town.

}

\newcommand{\myBcontent}[0]{
The Prague hotel is a 4-star hotel. It is older and smaller than the other hotels, but it has big bedrooms, and a large swimming pool. The price is 950 dollars. It is the cheapest hotel. There is a lot to do in Prague, and the hotel is crowded in summer. The hotel is half an hour from the center of the city by subway. And it is not close to the airport.

}

\newcommand{\myCcontent}[0]{
The island hotel is a very nice 5-star hotel. It is a large hotel and there are many large and small conference rooms. There are gardens and places to play golf, tennis and soccer, but not much else to do. The price is 1,350 dollars. The disadvantage of the hotel is that it is a long way from the airport, and you have to ride a boat to get there. The advantage is that it is quiet.

}

\newcommand{\myDcontent}[0]{
The Las Vegas hotel is a 5-star hotel. It looks great and has many bedrooms, large conference rooms and seminar rooms. The price is 1,950 dollars, the most expensive of the hotels. There are many things to do in Las Vegas, like shopping and sports, Guests can use hotel cars to go to these places and to get to the airport, which is close.

}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


