\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
getting ahead on the job
}

\newcommand{\myAcontent}[0]{
You are Eva, German, 42. You have a university degree in history, and worked for 15 years in Germany, the US and Poland in sales. You have been with Fast-Track for 1 year. You had a good sales record before, and a satisfactory one now. You speak German, English, Polish. You are quiet, and strong but nervous. You might be a good leader, but might be too dependent.
}

\newcommand{\myBcontent}[0]{
Fast-Track is looking for a new Polish Sales Manager. Sales are poor and staff is unmotivated. You want someone to increase sales and manage the sales team. He/She will be energetic, confident, outgoing, and have 1. a successful career in sales, 2. organization/interpersonal skills, 3. good academic record, 4. administrative ability, 5. knowledge of languages.
}

\newcommand{\myCcontent}[0]{
You are Barbara, Polish, 30. You finished high school and have a marketing diploma. You have been at Fast-Track for 12 years. You are the best sales rep in the Polish team. You know lots of English words, but are not very fluent. You are very strong, energetic, confident. But sometimes you appeared aggressive. You may not be a good team-player.
}

\newcommand{\myDcontent}[0]{
You are Tadeusz, Polish, 52. You have a university degree in engineering and worked in many industries before joining Fast-Track 5 years ago. You are sales manager for the south of Poland. You increased sales 12\% over the 5 years. You are very relaxed, but a hard worker. You are not creative, but are happy to use others' good ideas. People think you are practical and reliable.
}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


