\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
stress
}

\newcommand{\myAcontent}[0]{
So many people have lost their jobs. Now it is our turn to be fired. I am afraid I will be next. 

We are under a lot of pressure and there is never enough time to do a good job.

The stress is killing me. I just can't cope any more. 

}

\newcommand{\myBcontent}[0]{
The amount of pressure that management is trying to put on me is unbelievable. 

And I don't feel like I have any control over what is happening. It's a very stressful situation.

And management is not supportive. We are not told we are doing a good job. We are only blamed when management is unhappy.

I feel like I am falling off a cliff.

}

\newcommand{\myCcontent}[0]{
I can't focus on my work, because of the environment. I don't have my own space. 

Oh, I have a chair and a desk, but I have to share it. It is crowded and there are three other people, all in the same small space, with telephones ringing, people shouting, and others interrupting me. 

The computers and the air conditioning are noisy too. Often it's too hot in the office to work.  And I don't have my own computer.

}

\newcommand{\myDcontent}[0]{
Our manager is always giving us orders. She never listens to what we have to say.

When we ask her for something, she always says, 'No.' It's like talking to a brick wall. 

She also never tells us what management is thinking. If she told us more about what is happening, we would feel less stress.

She only criticizes us and blames us for things that are not our fault. She never says, 'Well done.' It's very demotivating.

}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{1}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{1}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{1}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{1}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{1}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{1}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{3}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{1}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


