\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
website negotiation
}

\newcommand{\myAcontent}[0]{
\\
You, together with B, are negotiating for Michelle, who is setting up an online bookstore. On the other hand, C and D are negotiating on behalf of the website designer. They represent the designer.\\\\
You want the website operating within one month. The quicker it is up, the better. But you realize the designer needs time to develop the site.\\\\
You want the website to have lots of information and different links that the user can click.\\\\
You want to pay the designer 6,000 dollars. This seems a reasonable amount of money. You think if you offer less than this, the designer won't be willing to do it, or won't do a good job.\\\\
You want to pay the designer when the site is finished and operating, so you can be sure it works and is acceptable.\\\\
You would like the site to show individual images of all the covers of the books that the bookstore sells. Images are always more interesting than text. They give the reader an idea of what the book is like.\\\\
You are willing to negotiate some of these requirements. But some of them are not negotiable. You aren't willing to compromise on them. B has the details. So, how will you change your position? And will C and D accept your position?\\\\

}

\newcommand{\myBcontent}[0]{
\\
You, together with A, are negotiating for Michelle, who is setting up an online bookstore. On the other hand, C and D are negotiating on behalf of the website designer. They represent the designer.\\\\
You are not willing to compromise on the time that A said. The site is very important to doing business. You are ready to send books to buyers, but the only way the buyers can contact you or even know you are doing business is through the web site. The quicker the site is up, the better.\\\\
You are not concerned about the amount of information on the site just now. You are ready to negotiate the number of pages and links on the site. In fact, any amount is okay.\\\\
You are not willing to pay more than the price A said. It is a fixed price which you can't negotiate.\\\\
You are ready to compromise on when the designer is paid, perhaps some in advance before the designer starts work, and some after the site is up and working.\\\\
A told C and D what Michelle wants in terms of the number of images and the amount of text on the site, but she is willing to compromise on this. She realizes that changes can be made later.\\\\
You don't have to change your position if C and D will accept what A said. But if they don't, you will have to negotiate some of those requirements. Which offers will C and D find unacceptable? And will C and D accept your new position?

}

\newcommand{\myCcontent}[0]{
\\
You, together with D, are negotiating for the designer, who sets up websites for online retailers. On the other hand, A and B are negotiating on behalf of Michelle, an online bookstore operator. They represent Michelle.\\\\
You want to take two months to get the website up and operating. Your reason it you have a lot of other work to do and you want to do a good job on Michelle's site, even though you realize she wants it up quickly.\\\\
You want to limit the amount of information on the website and the different links that the user can click. Michelle probably will want the site redesigned, and a simpler design will make redesigning easier. It will also be quicker to finish a simpler design.\\\\
You want to charge Michelle fifty dollars an hour. This seems a reasonable amount of money. It's the normal fee for the job.\\\\
You want to limit the size of the site. Rather than individual images of all the covers of all the books that the bookstore sells, you want to have bigger images of a few of the popular books. This will mean users don't have to wait so long to see the images.\\\\
You are willing to negotiate some of these requirements. But some of them may not be negotiable. You may not be willing to compromise on them. D has the details. So, how will you change your position? And will A and B accept your position?\\\\

}

\newcommand{\myDcontent}[0]{
\\
You, together with C, are negotiating for the designer, who sets up websites for online retailers. On the other hand, A and B are negotiating on behalf of Michelle, an online bookstore operator. They represent Michelle.\\\\
The designer is ready to agree the site be finished in a shorter time than the time C said he/she wanted to take. For example, he/she would be willing to have it ready in one month. But this would require some compromise by Michelle on the size of the site and the amount of information.\\\\
The designer is willing to incorporate Michelle's ideas into the design of the website, together with your ideas.\\\\
The designer is willing to be paid a fixed price rather than the way A mentioned. But in return, he/she would want half of the fee to be paid in advance, before starting work.\\\\
C told A and B about the problem of images. The designer however is willing to compromise on images, perhaps one or two images of individual covers of books on each page.\\\\
You don't have to change your position if A and B will accept what C said. But if they don't, you will have to negotiate some of those requirements. Which parts of your position will A and B find unacceptable? And will A and B accept your new position?

}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][14.1cm][c]{9.5cm}{%
	\hspace{0.1cm} \normalsize#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture3}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture4}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


