\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myAcontent}[0]{
At the Penske-Wynn showroom in Las Vegas, people didn't want to buy the cars. they just wanted to look at them. The problem was that there were lots of these people. Many Americans who aren't rich go to Las Vegas because they dream about winning lots of money. These people like to look at expensive cars.
}

\newcommand{\myBcontent}[0]{
Penske-Wynn started charging a 10 dollar entrance fee. People who said they weren't going to buy a Ferrari or Maserati, and who just wanted to look at the cars had to pay this 10 dollars. Children with their parents didn't have to pay. Ferrari clothes were also sold.
}

\newcommand{\myCcontent}[0]{
About one-fifth of the visitors said they were thinking of buying a car, so didn't have to pay. But there were so many visitors, the showroom was getting almost 100,000 dollars a month in admission fees. In addition, it was selling 20-30 cars a month.
}

\newcommand{\myDcontent}[0]{
The experiment was very successful. But other car showrooms may not be able to copy Penske-Wynn's solution. Other showrooms are not in Las Vegas. They do not have many visitors, and are not showing expensive cars to people who dream of being rich.
}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{3}{kroenke}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{3}{kroenke}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{3}{kroenke}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{3}{kroenke}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{3}{kroenke}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{3}{kroenke}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{3}{kroenke}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{3}{kroenke}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


