\documentclass[a4paper]{article}
\usepackage[cm]{fullpage}
\begin{document}

\large
18 April, 2003\\
A Valley mom awaits news of MIA son\\
by Macarena Hernandez\\
The San Antonio Express-News\\
LOS FRESNOS — Words can't describe the emotions Juanita Anguiano has experienced since learning her 24-year-old son was missing "somewhere in Iraq ." Juanita Anguiano, 45, of Los Fresnos, sits in her daughter's room near an altar she has built for her son, Edward Anguiano, 24, missing in action in Iraq since March 23.\\
\\
So the single mother, a teacher's aide, points to the ceiling fan he installed in her small living room. She points to the pinstriped couches, the tennis bracelet still in its red velvet case and the Martha Stewart patio furniture, all gifts from her first born and only son.  Her handyman, the man of her house.\\
\\
"I guess he had that, 'I have to help my sisters and my mom' " attitude, said Anguiano, 45. "He felt an obligation to me. I really depended on him. I didn't have anything here in this apartment. He bought me everything you see here. He bought me this lamp for Mother's Day. He bought me that on Christmas, the entertainment center."\\
..\\
"I wish I could talk to a mother who is in the same shoes as I am who has her son missing in action. It's very hard," said Anguiano, who speaks haltingly.  Her eyes are tired and swollen.\\
\\
"It's very confusing because of what I am hearing and that brings me down, but I don't let it," she added. "That's why I am trying not to watch too much television, especially the (stations) from Mexico , because they show a lot."\\
...\\
After graduating from Brownsville 's Hanna High School , he moved to Arkansas , where he worked at a poultry-packing plant and bought an old car. At 19, he never had taken a road trip alone, but he made it back safe, which gives Juanita Anguiano "faith my son is alive."\\
\\
After two years of college, he decided to leave the Valley to travel and earn some money to continue his education.  In August 2000, Anguiano enlisted in the Army. He served in Kosovo.\\
...\\
There have been many days, she says, when bad news wrecked her hope and sent it plunging. Sleep these days only comes with a pill. Votive candles burn day and night.  "I was happy because he wasn't among with the ones that were killed," Anguiano said. "Then it made me sad that he wasn't among the POWs and now I am back in the boat. But I don't give up hope because I know my son is alive. He is somewhere out there."\\
\\
She said she has moments when she can picture her son in some Iraqi village, like the ones she has seen on TV, surrounded by a herd of animals and the Iraqis he has befriended.\\
...\\
She fears she will learn of his death on TV, but a daughter, Rebecca, a high school sophomore, has reassured her that if anything happens, the Army will tell her first.\\
...\\
Rebecca often thinks of a night years ago when she was only 5. Rebecca and her brother rode in the back seat of a car with the windows rolled down.  "That's the memory I think about every day," she said. "He fell asleep and he was hugging me. And at that time, I felt nothing could ever harm me."\\
\end{document}
