\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{-0.02cm}{0.07cm} %HPDeskJet5160
% \textblockorigin{0.00cm}{0.00cm} %HPDeskJet5160
% \textblockorigin{-0.05cm}{0.13cm} %HPDeskJet5160
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\usepackage{multicol}
\usepackage{soul}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
present continuous 1
}

\newcommand{\myAcontent}[0]{
You call Elizabeth and say, "I'm divorcing Charles because he has been unfaithful to me." She asks you not to go ahead with it. You call Camilla and tell her, "I'm appearing on TV tomorrow night. I'm going to say you are to blame for the breakup of my marriage. I hate you."
}

\newcommand{\myBcontent}[0]{
Your mother, Elizabeth, calls you and tells you about Diana. You tell her, "I'm not going to contest the divorce. I love Camilla. She's getting a divorce from her husband and I'm going to marry her." You tell Camilla how happy you are now that Diana is divorcing you. You ask her how her divorce is going.
}

\newcommand{\myCcontent}[0]{
You tell call Charles and he says he's going to marry Camilla. You are mad. You say, "No king of England is going to marry a divorced woman."
}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\end{document}


