\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
kendall 1
}

\newcommand{\myAcontent}[0]{
The New Covent Garden Soup Company became very successful by selling fresh soups. It started off as a small company, but with the help of Kendall, it became a big company. Sales went from 3 million dollars to 30 million dollars. Everyone realized Kendall was a good businessman, but he also knew a lot about the food business. His parents were farmers.

}

\newcommand{\myBcontent}[0]{
When Kendall looked at other smaller food companies he could make into big companies, he noticed Green and Black Chocolates, which was owned by Craig Sams. Green and Black was small but he thought a lot of people were interested in organic food and unhappy with supermarket food. He decided to buy Green and Black from Craig Sams.

}

\newcommand{\myCcontent}[0]{
Many years ago, organic food wasn't popular. Although organic food was good for you, it didn't taste good. For many years, Craig Sams had tried to make a lot of money selling organic food, but he had never been very successful. Green and Block Chocolates was different, because people thought it was good for you AND it tasted good. Kendall thought he could make a lot of money with Sams' company.

}

\newcommand{\myDcontent}[0]{
At his first company, Kendall had tried to do everything himself. Later he said this was a mistake. He said managers need freedom to do things their way. He thought this makes them excited about their work. The owners have too much to think about, and don't have time to do their managers' work too. The owners should be thinking about the company's plans and what to do next. 

}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


