\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
kendall 4
}

\newcommand{\myAcontent}[0]{
Kendall's first jobs were as a lawyer and banker, but he was more interested in business. He helped the New Covent Garden Soup Company increase sales from 3 million dollars to 30 million dollars. He wanted to leave, but no-one wanted to buy the company. No-one could take his place. He was a good businessman, but he also knew a lot about the food business.

}

\newcommand{\myBcontent}[0]{
Before, organic food had been only eaten by a few people, but he saw his company's organic soups and Green and Black Chocolates were becoming very popular. This interested him. He thought that many people liked organic food because they didn't like supermarket food. He decided to buy the organic Green and Black Chocolates.

}

\newcommand{\myCcontent}[0]{
At the soup company, he learned that he must cooperate with big companies, rather than compete with them. so he can sell his company when he wants to leave. So he got a big company to invest in 5 percent of his company. When he sold the company to Cadbury's, many people who liked organic foods were unhappy. But that was his plan.

}

\newcommand{\myDcontent}[0]{
Teresa Graham said everyone needs to feel they own the business's plan by being involved in its creation. Kendall says something different: The business's owners need to give their managers freedom to do things their way. The owners have too much to think about, and don't have time to do their managers' work too. The owners should be thinking about planning the next move.

}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


