\documentclass[b5paper]{article}
\usepackage{color}
\usepackage{multicol}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.30cm}{0.35cm} %HPDeskJet5160
\textblockorigin{0.00cm}{0.15cm} %HPDeskJet5160
\setlength{\unitlength}{1cm}
\usepackage{xeCJK}
\setCJKmainfont{WenQuanYi Zen Hei}
\pagestyle{empty}

\newcommand{\myIdentifier}[0]{
Travel and hotel questions
}

\newenvironment{description*}%
{\begin{description}%
 \setlength{\itemsep}{0pt}%
 \setlength{\parsep}{0pt}%
 \setlength{\parskip}{0pt}}%
{\end{description}}

% \renewcommand{\labelitemi}{$\bullet$}

\newcommand{\myContent}[0]{

\setlength{\leftmargini}{+0.5cm}

\begin{multicols}{1}

\begin{description*}
  \item Are you afraid of going abroad alone?
  \item What was your best trip?
  \item What was your worst trip?
  \item Did your class in high school go on a trip together?
  \item Do you like to travel with your family? Why or why not?
  \item Do you prefer to travel by car, train, bus, plane or ship?
  \item Have you ever been in a difficult situation while traveling?
  \item Have you ever been on an airplane?
  \item Have you ever gotten lost while traveling? If so, tell about it?
  \item Have you ever taken a package tour?
  \item How many places have you been to?
  \item How much luggage do you usually carry?
  \item What is something you should not forget to take when you are traveling?
  \item If you went to X, what souvenirs would you buy?
  \item Do you prefer a budget or first class hotel? Why?
  \item Have you ever locked yourself out of your hotel room?
  \item The last time you traveled, how many people slept in the room?
  \item The last time you traveled, how many days did you stay at the hotel?
  \item Have you stayed at a hotel where you had to share the bathroom with other guests?
\end{description*}

\end{multicols}
}

\newcommand{\mycard}[2]{%
	\vspace{0.1cm}
	\large #1
	\par
	\begin{minipage}[c][11.9cm][c]{7.9cm}%
	\normalsize #2
	\end{minipage}
}

\begin{document}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{\myIdentifier}{\myContent} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture1}
\mycard{\myIdentifier}{\myContent} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{\myIdentifier}{\myContent}
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture5}
\mycard{\myIdentifier}{\myContent}
\end{textblock}

\end{document}


