\documentclass[b5paper]{article}
\usepackage{color}
\usepackage{multicol}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.30cm}{0.35cm} %HPDeskJet5160
\textblockorigin{0.00cm}{0.15cm} %HPDeskJet5160
\setlength{\unitlength}{1cm}
\usepackage{xeCJK}
\setCJKmainfont{WenQuanYi Zen Hei}
\pagestyle{empty}

\newcommand{\myIdentifier}[0]{
Cell phone survey
}

\newenvironment{itemize*}%
{\begin{itemize}%
 \setlength{\itemsep}{0pt}%
 \setlength{\parsep}{0pt}%
 \setlength{\parskip}{0pt}}%
{\end{itemize}}

\renewcommand{\labelitemi}{$\bullet$}

\newcommand{\myContent}[0]{

\setlength{\leftmargini}{+0.5cm}

\begin{multicols}{2}

\begin{itemize*}
\item Do you have a cell phone? A smart phone?
\item What is the name/brand of your phone?
\item What phone numbers can you find in the yellow pages of a phone book?
\item How can you find someone's telephone number on the Internet?
\item Have you ever called a business for information or to order something?
\item Have you ever had a problem with your phone bill/plan? What did you do?
\item Have you ever dialed the wrong number? Did you feel frustrated or embarrassed?
\item Have you ever left a voice mail or a message on an answering machine?
\item What is good telephone etiquette? What is considered rude in your culture?
  \item How many phone calls do you usually receive and make in one day?
  \item How many in your family have a mobile?
  \item What cellphone company do you use? Why? For how long? Is it OK?
  \item About how many text messages do you send in a day?
  \item Who pays for your phone? The bill is ..?
  \item What features does your cell phone have?
  \item Do you know how to use all the functions on your phone?
  \item How long have you had a cell phone?
        Or, why have you decided not to have one?
  \item When should you turn your phone off?
  \item Do people' phones ever bother you?
  \item What are the dis/advantages of cells?
  \item Could you live without your mobile?
  \item When did you first get a cell phone?
  \item Have your parents ever been angry with you because of your phone use?
  \item At what age do kids now get cell phones? At what age should they be allowed to?
  \item Have you ever tried getting a date with your phone?
  \item Who do you call with your cell phone? Who calls you on your phone?
  \item Your most expensive call ever was ..
  \item Is it OK to have your cell on in class?
  \item Is it illegal to speak on your cell phone while driving? Do you think it should be?
  \item Has your phone ever been lost or stolen?
  \item Has your cell phone ever broken down?
  \item Do you ever just let the phone ring?
  \item What are the health risks of phones?
  \item Have you bullied/been bullied with a cell?
  \item Will these risks stop you from using a cell?
  \item People feel pressure to renew their phone to the newest model. Do you?
\end{itemize*}

\end{multicols}
}

\newcommand{\mycard}[2]{%
	\vspace{0.1cm}
	\large #1
	\par
	\begin{minipage}[c][11.9cm][c]{14.1cm}%
	\normalsize #2
	\end{minipage}
}

\begin{document}

\begin{textblock}{16}(0,0)
\textblocklabel{picture1}
\mycard{\myIdentifier}{\myContent} 
\end{textblock}

\begin{textblock}{16}(0,8)
\textblocklabel{picture5}
\mycard{\myIdentifier}{\myContent}
\end{textblock}

\end{document}


