\documentclass[a4paper]{article}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.30cm}{0.35cm} %HPDeskJet5160
\textblockorigin{0.00cm}{0.15cm} %HPDeskJet5160
\setlength{\unitlength}{1cm}
\usepackage{xeCJK}
\setCJKmainfont{WenQuanYi Zen Hei}
\pagestyle{empty}

\newcommand{\myIdentifier}[0]{
Food and Restaurants
}

\newenvironment{itemize*}%
{\begin{itemize}%
 \setlength{\itemsep}{0pt}%
 \setlength{\parsep}{0pt}%
 \setlength{\parskip}{0pt}}%
{\end{itemize}}

\renewcommand{\labelitemi}{$\bullet$}

\newcommand{\myContent}[0]{

\setlength{\leftmargini}{-0.5cm}

\begin{description}

\item [Questions about food]\

\begin{itemize*}
\item Have you had/Did you have lunch?/Do you eat lunch?
\item What kind of food do you like to eat?/is your favorite?
\item Can you tell/ask us about some food you know?
\end{itemize*}

\item [Fruit guessing game]\

\begin{description}
\item One person describes a fruit in English. The others try to guess what the fruit is.
eg passionfruit, bananas, mangos, apples. `It's green, or yellow. It's long and thin ..'
\end{description}

\item [The 4 snack food groups]\

\begin{description}
\item Crunchy, chewy, creamy and bready.
\end{description}

\item [Questions about restaurants]\
	\begin{itemize*}
	\item Do you eat out a lot?
	\item What are the different kinds/names of restaurants?
	\item Tell us where/how/what you eat everyday at school/home.
	\end{itemize*}

\item [What to say at an expensive restaurant]\
	\begin{enumerate}
	\item 预约
	\item 进入餐厅
	\item 决定吃什么
	\item 订餐
	\item 甜点
	\item 要求检查/该法案要求
	\item 小费
	\end{enumerate}

\end{description}
}

\newcommand{\mycard}[2]{%
	\vspace{0.1cm}
	\large #1
	\par
	\begin{minipage}[c][14.4cm][c]{9.1cm}%
	\normalsize #2
	\end{minipage}
}

\begin{document}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{\myIdentifier}{\myContent} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{\myIdentifier}{\myContent}
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{\myIdentifier}{\myContent}
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{\myIdentifier}{\myContent} 
\end{textblock}

\end{document}


