\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myAcontent}[0]{
He thought he could make money on the Internet by selling advertising space on his website. Some friends and some of his family gave him some money for the first few advertisements. He used the money to promote the site. Although his idea looks very simple and easy, he had to work very hard to advertise the site.
}

\newcommand{\myBcontent}[0]{
He contacted lots of television and newspaper companies about his idea, and people were very interested in listening to him talk. He hired a person to contact TV and newspaper companies in the US for him. He went to the US for one week and appeared on television there.
}

\newcommand{\myCcontent}[0]{
All the space on his site was sold and he made one million dollars. A few advertisers on the site were well-known, like Yahoo. But most of the advertisers are not well-known and their services are not good. For example, dating services, Internet gambling and free download sites.
}

\newcommand{\myDcontent}[0]{
The website was criticized because the services of the advertisers on it were not good. Some people could not understand why advertisers were attracted by the website. Others said that he made too much money too quickly. He said that he needed the money to go to college, but one million dollars was too much.
}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{3}{kroenke}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{3}{kroenke}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{3}{kroenke}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{3}{kroenke}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{3}{kroenke}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{3}{kroenke}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{3}{kroenke}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{3}{kroenke}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


