\documentclass[a4paper]{article}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
\textblockorigin{0.00cm}{+0.15cm} %HP DeskJet 5160
\usepackage{xeCJK}
\setCJKmainfont{AR PL Mingti2L Big5}
\newfontfamily\IPAfont{Gentium}
\usepackage{rotating}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newenvironment{itemize*}%
{\begin{itemize}%
 \setlength{\itemsep}{0.0cm}%
 \setlength{\parsep}{0pt}%
 \setlength{\parskip}{0pt}}%
{\end{itemize}}

\newcommand{\mycard}[3]{%
	\small #1 #2
	\par
	\parbox[t][6.8cm][c]{9.5cm}{%
	\par
	\myleft{#3}
	\par
	\myright{#3}
	}
}

\newcommand{\myleft}[1]{%
	\begin{sideways}
	\hspace*{-0.9cm}
		\parbox[t][2.7cm][t]{6.5cm}{%
		\Large #1
		}
	\end{sideways}
}

\newcommand{\myright}[1]{%
	\hspace*{6.5cm}
	\begin{turn}{270}
	\hspace*{-7.1cm}
		\parbox[t][2.7cm][t]{6.5cm}{%
		\Large #1
		}
	\end{turn}
}

\begin{document}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{3}{chemists, maps and family}{
\begin{itemize*}
\item The chemists are \textbf{doing/performing} an experiment.
\item They are \textbf{taking part} in a competition. They may \textbf{win} the competition.
\end{itemize*}
}
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{3}{chemists, maps and family}{
\begin{itemize*}
\item They \textbf{have to wear} protective clothing and glasses.
\item Something may
\begin{itemize*}
\item \textbf{hurt their eyes},
\item \textbf{cause some injury to}, or \textbf{injure} their bodies,
\item or \textbf{ruin} their clothes.
\end{itemize*}
\end{itemize*}
}
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{3}{chemists, maps and family}{
\begin{itemize*}
\item Chemicals can \textbf{stain} clothes and skin. Blood can leave bloodstains.
\end{itemize*}
}
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{3}{chemists, maps and family}{
\begin{itemize*}
\item Two women /wɪmɪn/ are thinking about where to locate a new building.
\end{itemize*}
}
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{3}{chemists, maps and family}{
\begin{itemize*}
\item Pron <area>: /ˈeəɹiə/ ~ (US) /ˈæɹiə/
\item http://commons.wikimedia.org/wiki/File:En-us-area.ogg
\item http://en.wiktionary.org/wiki/area
\end{itemize*}
}
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{3}{chemists, maps and family}{
\begin{itemize*}
\item They may \textbf{make} many people move.
\item They may \textbf{force} many people \textbf{to} move.
\item NOT: They may \textbf{let} many people move.
\end{itemize*}
}
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{3}{chemists, maps and family}{
\begin{itemize*}
\item The family never feels \textbf{bored}. (NOT: boring)
\item The thing which causes the experience is \textbf{boring, exciting, tiring, amusing}, etc.
\item The person which is affected by the thing is \textbf{bored, excited, tired, amused}, etc
\end{itemize*}
}
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{3}{chemists, maps and family}{
\begin{itemize*}
\item The experience \textbf{brings the family together}.
\end{itemize*}
}
\end{textblock}

\null
\newpage

\end{document}


