\documentclass[b5paper]{article}
\usepackage{color}
\usepackage{multicol}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.30cm}{0.35cm} %HPDeskJet5160
\textblockorigin{0.00cm}{0.15cm} %HPDeskJet5160
\setlength{\unitlength}{1cm}
\usepackage{xeCJK}
\setCJKmainfont{WenQuanYi Zen Hei}
\pagestyle{empty}

\newcommand{\myIdentifier}[0]{
Language survey
}

\newenvironment{enumerate*}%
{\begin{enumerate}%
 \setlength{\itemsep}{0pt}%
 \setlength{\parsep}{0pt}%
 \setlength{\parskip}{0pt}}%
{\end{enumerate}}

% \renewcommand{\labelitemi}{$\bullet$}

\newcommand{\myContent}[0]{

\setlength{\leftmargini}{+0.5cm}

\begin{multicols}{3}

\begin{enumerate*}
\item    What language is spoken the most here?
\item    Is there a second language in Taiwan?
\item    Does Chinese adopt words from English?
\item    Is English important in Taiwan?
\item    Why are you studying English?
\item    What language do you like speaking in?
\item    What language do you least like using?
  \item  What's the native language spoken in China? Brazil? Switzerland? Australia? Canada?
  \item  The strangest language you've heard is ..?
  \item  Do you wish your country had another language instead of the present one?
  \item  Do you have pen-friends? If yes, what languages do they speak?
  \item  Name some languages that are no longer spoken?
  \item  What would you do traveling if no-one spoke Chinese or English?
  \item  Should disappearing languages be protected?
  \item  What languages are spoken the most throughout the world?
  \item  Which do you think is the most difficult language?
  \item  How many languages do you speak?
  \item  Do you know anyone who is monolingual?
  \item  Do you know anyone who is bilingual or multilingual?
  \item  Would you like to raise multilingual children?
  \item  What are the disadvantages of being monolingual?
  \item  Have you been somewhere where most people speak only one language?
  \item  Have you been somewhere where most people speak more than one language?
  \item  Does your country have official languages? What languages are official?
  \item  What other languages are spoken by minority groups and foreign workers?
\end{enumerate*}

\end{multicols}
}

\newcommand{\mycard}[2]{%
	\vspace{0.1cm}
	\large #1
	\par
	\begin{minipage}[c][11.9cm][c]{16.1cm}%
	\normalsize #2
	\end{minipage}
}

\begin{document}

\begin{textblock}{16}(0,0)
\textblocklabel{picture1}
\mycard{\myIdentifier}{\myContent} 
\end{textblock}

\begin{textblock}{16}(0,8)
\textblocklabel{picture5}
\mycard{\myIdentifier}{\myContent}
\end{textblock}

\end{document}


