\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
stress measures 1
}

\newcommand{\myAcontent}[0]{
To reduce stress, the company should give workers free medical checkups each year. It should also identify stress hotspots by asking Alan Bradshaw, or someone, to come and check. The company nurse cannot identify stress hotspots. The nurse does not know where stress is worst at the company.
}

\newcommand{\myBcontent}[0]{
Some foods reduce stress. Some foods increase stress. The company should not provide drinks like coffee, coke and other stimulants, which increase stress. Workers can buy coffee if they want it. In the company restaurant, there should be food which reduces stress, rather than increases it. Natural foods may decrease stress. So there should be natural food in the restaurant.
}

\newcommand{\myCcontent}[0]{
When you are feeling stress, exercise is a good way of reducing stress. The company should allow workers to play basketball during the lunch break to reduce stress. It should also give workers free membership in the local sports center so they can go swimming or lift weights. Many workers would enjoy swimming after work.
}

\newcommand{\myDcontent}[0]{
A company tour every month would reduce stress. Workers with their families would travel together to an interesting place. They would not discuss work. They should forget about work, and have fun with each other. Once or twice a year, they could travel together overseas. This should not be for a company conference, where they discuss work. It should be just for relaxation.
}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


