\documentclass[b5paper]{article}
\usepackage{color}
\usepackage{multicol}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.30cm}{0.35cm} %HPDeskJet5160
\textblockorigin{0.00cm}{0.15cm} %HPDeskJet5160
\setlength{\unitlength}{1cm}
\usepackage{xeCJK}
\setCJKmainfont{WenQuanYi Zen Hei}
\pagestyle{empty}

\newcommand{\myIdentifier}[0]{
Movies questions
}

\newenvironment{enumerate*}%
{\begin{enumerate}%
 \setlength{\itemsep}{0pt}%
 \setlength{\parsep}{0pt}%
 \setlength{\parskip}{0pt}}%
{\end{enumerate}}

% \renewcommand{\labelitemi}{$\bullet$}

\newcommand{\myContent}[0]{

\setlength{\leftmargini}{+0.5cm}

\begin{multicols}{3}

\begin{enumerate*}
  \item What kinds of movies do you like/dislike?
  \item Do you usually watch movies at home or at a movie theater?
  \item Have you ever seen the same movie more than once?
  \item Have you ever seen (movie name)?
  \item How often do you go to movies?
  \item How often do you rent videos?
  \item What was the best/worst/scari-
  est/funniest/most romantic movie you have seen?
  \item What was the last movie you saw?
  \item Which do you like better, action movies or comedy movies?
  \item Who is your favorite actor or actress?
  \item Is there a movie you could watch over and over again?
  \item How much does it cost to see a movie?
  \item How much do you spend on buying/renting DVDs?
  \item How much money do you spend when you go to the movies?
  \item Which do you prefer, animated movies or real movies?
  \item What is your favorite movie soundtrack?
  \item Who is your favorite movie hero?
  \item What do you think about comic book movies?
  \item What is your favorite classical movie?
  \item Which do you prefer, comedy movies or horror movies?
  \item Have you ever watched a movie twice that you disliked?
  \item Have you ever fallen asleep in the middle of a film? Why?
  \item Do you ever download bootleg movies?
  \item Do you like watching movies in English or Chinese?
  \item Do you choose a film for the plot/story or the actors?
  \item Do you usually choose which films to watch?
  \item If you decide to rent a movie, how do you choose one?
  \item Who chooses the programs the family watches together?
  \item Who holds the remote in your family?
  \item If two people want to watch different programs at the same time, how do you choose?
  \item What kind of movie would you like to star in? Why?
  \item Do you think there should be more Taiwanese movies?
  \item What is something that you happens too often or never happens in a movie?
  \item Is there too much nudity/violence in movies, or not enough?
  \item Do people talk/eat in movie theaters here? What do they eat?
  \item What movie ratings are enforced in your country?
  \item Are movie trailers common in Taiwan?
\end{enumerate*}

\end{multicols}
}

\newcommand{\mycard}[2]{%
	\vspace{0.1cm}
	\large #1
	\par
	\begin{minipage}[c][11.9cm][c]{16.1cm}%
	\normalsize #2
	\end{minipage}
}

\begin{document}

\begin{textblock}{16}(0,0)
\textblocklabel{picture1}
\mycard{\myIdentifier}{\myContent} 
\end{textblock}

\begin{textblock}{16}(0,8)
\textblocklabel{picture5}
\mycard{\myIdentifier}{\myContent}
\end{textblock}

\end{document}


