\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{0.10cm}{1.00cm}
\textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myIdentifier}[0]{
William Kendall
}

\newcommand{\myAcontent}[0]{
His parents were successful farmers. And his first jobs were as a lawyer and banker, but he decided he was more interested in business. At the New Covent Garden Soup Company, he became CEO, and sales went from 3 million dollars to 30 million dollars. He wanted to leave, but no-one wanted to buy the company. No-one could take his place. He was too good a businessman.

}

\newcommand{\myBcontent}[0]{
Organic food had been only eaten by a few people, but he saw his company's organic soups and Green and Black Chocolates were becoming very popular. This interested him. He thought that people eating organic food felt they were closer to the source of their food. He decided to buy the organic Green and Black Chocolates from Craig Sams and try marketing it to not just people interested in organic food, but everyone.

}

\newcommand{\myCcontent}[0]{
At the soup company, he learned that he must have a cooperative relationship with a large company so that he can sell his company easily after it is successful and he wants to leave. So he got a big chocolate company to invest in 5 percent of his company. Some believers in organic food weren't happy with that. When he sold all his shares to Cadbury's, many were suprised and some were even unhappier.

}

\newcommand{\myDcontent}[0]{
Teresa Graham said everyone needs to feel they own the business's plan by being involved in its creation. Kendall says something different: The business's owners need to give their managers freedom to do things their way. The owners have too much to think about, and don't have time to do their managers' work too. The owners should be thinking about planning the next move.

}

\newcommand{\mycard}[5]{%
	\vspace{0.1cm}
	\small #1 #2
	\par
	\parbox[t][6.7cm][c]{9.5cm}{%
	\hspace{0.1cm} \Large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture4}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{A:
\myAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{B:
\myBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{C:
\myCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture8}
\mycard{1/1}{\myIdentifier}{\parbox{9.0cm}{D:
\myDcontent
}}{}{} 
\end{textblock}

\end{document}


